\begin{thebibliography}{5}
%%%%%%%%%%% 1
\bibitem{l1}
Sonal Patil, Shrutilipi Bhattacharjee, and Soumya K. Ghosh. \textquotedblleft A spatial web crawler for discovering geo-servers and semantic referencing with spatial features\textquotedblright.\ In \textit{International Conference on Distributed Computing and Internet Technology}, pp. 68-78. Springer International Publishing, 2014.

%%%%%%%%% 
\bibitem{l2}
Li, Wenwen, Chaowei Yang, and Chongjun Yang. \textquotedblleft An active crawler for discovering geospatial web services and their distribution pattern - A case study of OGC Web Map Service\textquotedblright.\ \textit{International Journal of Geographical Information Science} 24, no. 8 (2010): 1127-1147.

%%%%%%%%%%%
\bibitem{l3}
Najork, Marc.\textquotedblleft Web crawler architecture\textquotedblright.\ In \textit{Encyclopedia of Database Systems}, pp. 3462-3465. Springer US, 2009.

%%%%%%%%%%% may not be useful
\bibitem{l4}
Ahlers, Dirk, and Susanne Boll.\textquotedblleft Location-based Web search\textquotedblright.\ In \textit{The Geospatial Web}, pp. 55-66. Springer London, 2009.

%%%%%%%%%%%
\bibitem{l5}
Li, W., C. Yang, D. Nebert, R. Raskin, P. Houser, H. Wu, and Z. Li.\textquotedblleft Semantic-based web service discovery and chaining for building an Arctic spatial data infrastructure\textquotedblright.\ \textit{Computers \& Geosciences} 37, no. 11 (2011): 1752-1762.

%%%%%%%%%%%
\bibitem{l6}
Jiang, Jun, Chong-jun Yang, and Ying-chao Ren.\textquotedblleft A spatial information crawler for opengis wfs\textquotedblright.\ In \textit{Sixth International Conference on Advanced Optical Materials and Devices}, pp. 71432C-71432C. International Society for Optics and Photonics, 2008.

%%%%%%%%%%%
\bibitem{l7}
\textit{http://geopython.github.io/pycsw-workshop/}

\bibitem{l8}
\textit{https://geopython.github.io/OWSLib/}

%%%%%%%%%%%
\bibitem{l9}
Lopez-Pellicer, Francisco J., et al.
\textquotedblleft Discovering geographic web services in search engines\textquotedblright.\
\textit{Online Information Review} 35.6 (2011): 909-927.

\bibitem{l10}
\textit{https://github.com/geoserver/geoserver}

\bibitem{l11}Yiu, Man Lung, Hua Lu, Nikos Mamoulis, and Michail Vaitis.\textquotedblleft Ranking spatial data by quality preferences\textquotedblright.\ \textit{IEEE Transactions on Knowledge and Data Engineering} 23, no. 3 (2011): 433-446.

\bibitem{l12}
Hjaltason, Gisli, and Hanan Samet.\textquotedblleft Ranking in spatial databases\textquotedblright.\ In \textit{Advances in Spatial Databases}, pp. 83-95. Springer Berlin/Heidelberg, 1995.

\bibitem{l13}
\textit{https://github.com/karimbahgat/Pyqtree}

\bibitem{l14}
Paul, Manoj, and S. K. Ghosh.\textquotedblleft An approach for service oriented discovery and retrieval of spatial data\textquotedblright.\ In \textit{Proceedings of the 2006 international workshop on Service-oriented software engineering}, pp. 88-94. ACM, 2006.

\bibitem{l15}
Nogueras-Iso, Javier, Francisco Javier Zarazaga-Soria, Ruben Bejar, P. J. Alvarez, and Pedro R. Muro-Medrano.\textquotedblleft OGC Catalog Services: a key element for the development of Spatial Data Infrastructures\textquotedblright.\ \textit{Computers \& Geosciences} 31, no. 2 (2005): 199-209.

\bibitem{l16}
Jones, Christopher B., Alia I. Abdelmoty, David Finch, Gaihua Fu, and Subodh Vaid.\textquotedblleft The SPIRIT spatial search engine: Architecture, ontologies and spatial indexing\textquotedblright.\ In \textit{International Conference on Geographic Information Science}, pp. 125-139. Springer Berlin Heidelberg, 2004.

\bibitem{l17}
Lopez-Pellicer, Francisco J., Aneta J. Florczyk, Ruben Bejar, Pedro R. Muro-Medrano, and F. Javier Zarazaga-Soria.\textquotedblleft Discovering geographic web services in search engines\textquotedblright.\ \textit{Online Information Review} 35, no. 6 (2011): 909-927.

\end{thebibliography}

%%%%%%%%%%%
% \bibitem{latexcompanion8}
% Suakanto, Sinung, et al.
% \textit{Building crawler engine on cloud computing infrastructure.}
% Cloud computing and social networking (ICCCSN), 2012 international conference on. IEEE, 2012.