\chapter{Literature Survey}

The introduction of the coverage problems in wireless sensor networks is briefly discussed in the previous chapter. This chapter goes to the details of the wide range of works already done in this area and its advantage, improvements done by other researchers are discussed. The three main classes of coverage in WSN such as area coverage, point coverage and barrier coverage are discussed in detail. Various works done in the field of sweep coverage in wireless sensor networks particularly in point coverage is discussed. The definitions and studies in area sweep coverage in mobile wireless sensor networks is discussed in the last section.

Bang Wang \cite{wang2011coverage} defined the sensor coverage as follows. Sensor coverage models are abstraction models trying to quantify how well sensors can sense physical phenomena at some location, or in other words, how well sensors can cover such locations. Network sensing coverage, on the other hand, can be considered as a collective measure of the quality of service provided by sensor nodes at different geographical locations.

\section{Area Coverage}

\subsection{Area Coverage in MWSN}

\section{Target Coverage}

\section{Barrier Coverage}

\section{Sweep Coverage}

\subsection{Area Sweep Coverage}



%Sweep Period \cite{yang2013sweep}
%Sweep coverage either by sleep scheduling or by mobility.\\
%Point Sweep Coverage \cite{wang2011coverage} Discussion\cite{gorain2015approximation}
%all\cite{yang2013sweep}
%
%
%Difference between deployment point and docking station.\\ 
%Extensive discussion about all the works in this area.



