\addcontentsline{toc}{chapter}{\numberline{}Acknowledgments}
 \vspace*{.5cm}
 \centerline{\LARGE \textsc{\textbf{Acknowledgement}}}
 \vspace*{.5cm}
 \vspace*{1cm}
 %\thispagestyle{plain}
 %\onehalfspace
\hspace*{0.6cm}First and foremost, I would like to express my deepest gratitude and sincere thanks to my advisor, \emph{\textbf{Prof. Soumya K. Ghosh}} for his inspiration, encouragement and able guidance all throughout the course of my M.Tech Project. It is because of his valuable advice from time to time and constant support that today I have been able to give shape to my work. It is indeed an honour and a great privilege for me to have worked under his guidance which has made my research experience productive. I learned an approach of humanity, perseverance and patience from him. 
\vskip 0.1in
\hspace*{0.6cm}I sincerely acknowledge my deepest gratitude towards all faculty members of Department of Computer Science \& Engineering for providing in-depth knowledge on various
subjects over the past two years. It was a pleasure to learn and work with their
co-operation.
\vskip 0.1in
\begin{comment}
\hspace*{0.6cm}Lastly and most importantly, I am grateful to my beloved father \emph{\textbf{Naresh chandra kumar}} and my beloved mother \emph{\textbf{Krishna kumari}} for their unconditional love and constant encouragement which has given me the strength to complete this thesis.
\end{comment}
\vspace*{2cm}
\begin{flushleft}
\vspace{0.5cm} Dated:
\end{flushleft}
\begin{flushright}
\hspace{3cm}
\begin{tabular}{l}
	\tabularnewline 
	\hline Punjabi Deepak Bharatbhai
	\tabularnewline
\end{tabular} \\
\hspace{3cm} Department of Computer Science \& Engineering, \\
\hspace{3cm} Indian Institute of Technology, Kharagpur.\\
\end{flushright}

