\addcontentsline{toc}{chapter}{\numberline{}Declaration}
\begin{spacing}{1.07}
\begin{center}
\vspace*{0.1cm}
\vskip 0.1in
\textbf{ \Large \underline{DECLARATION}}
\vskip 0.05in
\vskip 0.1in
\vskip 0.2in
\end{center}
\vskip 0.1in
I, \textbf{Punjabi Deepak Bharatbhai}, Roll No.\textbf{15IT60R17}, registered as a student of M.Tech. program in the Department of Computer Science \& Engineering, Indian Institute of Technology, Kharagpur, India (hereinafter referred to as the 'Institute') do hereby submit my thesis, title: \textbf{Spatial Data: Crawling, Metadata Discovery, Publishing \& Query Orchestration} (hereinafter referred to as 'my thesis') in a printed as well as in an electronic version for holding in the library of record of the Institute.
\vskip 0.1in
\begin{flushleft}
I hereby declare that:
\end{flushleft}
\hspace*{0.6cm}1. The electronic version of my thesis submitted herewith on CDROM is in PDF format.
\vskip 0.1in
2. My thesis is my original work of which the copyright vests in me and my thesis does not infringe or violate the rights of anyone else.\vskip 0.1in
3. The contents of the electronic version of my thesis submitted herewith are the same as that submitted as final hard copy of my thesis after my viva voice and adjudication of my thesis on 03-05-2017.\vskip 0.1in
4. I agree to abide by the terms and conditions of the Institute Policy on Intellectual Property (hereinafter 'Policy') currently in effect, as approved by the competent authority of Institute.\vskip 0.1in
5. I agree to allow the Institute to make available the abstract of my thesis in both hard copy (printed) and electronic form.
\vskip 0.1in6. For the Institute's own, non-commercial, academic use I grant to the Institute the non-exclusive license to make limited copies of my thesis in whole or in part and to loan such copies at the Institute's discretion to academic persons and bodies approved of from time to time by the Institute for non-commercial academic use. All usage under this clause will be governed by the relevant fair use provisions in the Policy and by the Indian Copyright Act in force at the time of submission of the thesis.
\vskip 0.1in7. Furthermore\newline
\hspace*{1.7cm}(a) I agree to allow the Institute to place such copies of the electronic version of my  thesis on the private Intra-net maintained by the Institute for its own academic community.\newline
\hspace*{1.7cm}(b) I agree to allow the Institute to publish such copies of the electronic version of my thesis on a public access website of the Internet should it so desire.
\vskip 0.1in8. That in keeping with the said Policy of the Institute I agree to assign to the Institute (or its Designee/s) according to the following categories all rights in inventions, discoveries or rights of patent and/or similar property rights derived from my thesis where my thesis has been completed:\vskip 0.1in
\hspace*{1cm}a. with use of Institute-supported resources as defined by the Policy and revisions thereof,\newline
\hspace*{1.6cm}b. with support, in part or whole, from a sponsored project or program, vide clause 6(m) of the Policy.\newline \newline
\hspace*{1.1cm}I further recognize that:\vskip 0.05in
\hspace*{1cm}c. All rights in intellectual property described in my thesis where my work does not qualify under sub-clauses 8(a) and/or 8(b) remain with me.
\vskip 0.1in9. The Institute will evaluate my thesis under clause 6(b1) of the Policy. If intellectual property described in my thesis qualifies under clause 6(b1) (ii) as Institute-owned intellectual property, the Institute will proceed for commercialization of the property under clause 6(b4) of the Policy. I agree to maintain confidentiality as per clause 6(b4) of Policy.
\vskip 0.1in10. If the Institute does not wish to file a patent based on my thesis, and it is my opinion that my thesis describes patentable intellectual property to which I wish to restrict access, I agree to notify the Institute to that effect. In such a case no part of my thesis may be disclosed by the Institute to any person(s) without my written authorization for one year after the date of submission of the thesis or the period necessary for sealing the patent, whichever is earlier.
%\vskip 1in
\newline
\vspace{1cm} \hfill
\begin{flushright}
\begin{tabular}{l} \tabularnewline
\hline
Punjabi Deepak Bharatbhai
\tabularnewline
\end{tabular}\\
\hspace{3cm} Department of Computer Science \& Engineering,\\
\hspace{3cm} Indian Institute of Technology, Kharagpur.\\
\end{flushright}

\end{spacing}
